Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
dataflow refs
the prefix order (to define monotonicity)

\newcommand{\kstar}{^{\textstyle *}}

@@

Nodes $f$ of the graph represent functions from one (possibly empty)
input stream to an output stream $f : D\kstar \to D\kstar$. $D$
represents the basic data type of a line of characters. This
representation captures the majority of shell commands. The nodes are
monotonic, meaning that they cannot retract their output. More
formally, $\forall f, x, y, f(x) = y$, then for any $x'$, there exists
$y'$ such that $f(x.x') = y.y'$, where $.$ is standard concatenation
and will be omitted when obvious. An example of a node is the
following command:

@@

>>>>

\newcommand{\kstar}{^{\textstyle *}}
\newcommand{\eps}{\varepsilon}

@@

For a set $D$, we write $D\kstar$ to denote the set of all finite
words over $D$. For words $x, y \in D\kstar$, we write $x \cdot y$
or $xy$ to denote their concatenation. We write $\eps$ for the empty
word. We say that $x$ is a \emph{prefix} of $y$, and we write $x \leq y$, if there is a word $z$ such that $y = xz$. It is easy to see that $\leq$ is a partial order, and it is often referred to as the \emph{prefix order}.

A node $f$ of the graph represents a function from one (possibly empty)
input stream to an output stream $f : D\kstar \to D\kstar$, where $D$
represents the basic data type of a line of characters. This
representation captures the majority of shell commands. We require that
the function $f$ is monotone w.r.t.\ the prefix order. This captures
the idea that a node cannot retract output after it has been emitted.
%More formally, $\forall f, x, y, f(x) = y$, then for any $x'$, there exists $y'$ such that $f(x.x') = y.y'$, where $.$ is standard
%concatenation and will be omitted when obvious.
An example of a node is the following command:

@@

\km{Some very early references on the dataflow model of computation (maybe there are relevant?): \cite{KM1966, D1974Dataflow, K1974KPN, KMacQ1977}}
